A Comparison of Graph Processing Systems

### 2020-09-16 documentation/paper/sections/results/sssp.tex
table styling

\begin{table}
\renewcommand{\arraystretch}{1.2}
\tiny
\centering
\caption{Distributed SSSP Execution Times and Their Realation to Galois Push}
\begin{tabular}{crrrrrrrr}
\hline
\bf{Data Set}&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
&$\times$&(s)&$\times$&(s)&$\times$&(s)&$\times$&(s)\\\hline
flickr & 1.0 & (2.4) & 0.97 & (2.4) & 1.02 & (2.5) & 17.46 & (42.6)\\
orkut & 1.0 & (4.2) & 1.28 & (5.4) & 4.12 & (17.3) & 14.38 & (60.4)\\
wikipedia & 1.0 & (14.2) & 1.88 & (26.6) & 5.26 & (74.5) & 7.11 & (100.8) \\
twitter & 1.0 & (40.0) & 3.56 & (142.2) & 9.79 & (391.1) & 8.76 & (349.9)\\
rMat27 & 1.0 & (39.0) & 3.98 & (154.9) & 9.91 & (386.0) & 14.52 & (565.8)\\
friendster & 1.0 & (58.5) & 2.32 & (136.0) & 9.72 & (568.9) & 7.59 & (444.0)\\
rMat28 & 1.0 & (71.5) & 5.7 & (407.9) & 11.07 & (792.0) & 16.5 & (1180.2)\\\hline
\end{tabular}
\label{tbl:ssspexec}
\end{table}

>>>>

\begin{table}
\renewcommand{\arraystretch}{1.2}
\tiny
\centering
\caption{Distributed SSSP Execution Times and Their Realation to Galois Push}
\begin{tabular}{crrrrrrrr}
\toprule
\bf{Data Set}&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
&$\times$&(s)&$\times$&(s)&$\times$&(s)&$\times$&(s)\\\midrule
flickr & 1.0 & (2.4) & 0.97 & (2.4) & 1.02 & (2.5) & 17.46 & (42.6)\\
orkut & 1.0 & (4.2) & 1.28 & (5.4) & 4.12 & (17.3) & 14.38 & (60.4)\\
wikipedia & 1.0 & (14.2) & 1.88 & (26.6) & 5.26 & (74.5) & 7.11 & (100.8) \\
twitter & 1.0 & (40.0) & 3.56 & (142.2) & 9.79 & (391.1) & 8.76 & (349.9)\\
rMat27 & 1.0 & (39.0) & 3.98 & (154.9) & 9.91 & (386.0) & 14.52 & (565.8)\\
friendster & 1.0 & (58.5) & 2.32 & (136.0) & 9.72 & (568.9) & 7.59 & (444.0)\\
rMat28 & 1.0 & (71.5) & 5.7 & (407.9) & 11.07 & (792.0) & 16.5 & (1180.2)\\\bottomrule
\end{tabular}
\label{tbl:ssspexec}
\end{table}
